Brundle Development

### 2017-11-28 Manuscript_Figures.Rmd
Markdown updated

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, messages=FALSE)
```

@@

@@

@@

@@

@@

```{r,results='hide', message=FALSE, warning=FALSE}
#Check CTCF

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, messages=FALSE, cache=TRUE)
```

@@

Comparison of fold-change of H4 acetylation (Lys12) before and after treatment with estradiol.  MA plot of H4K12ac after normalisation to CTCF binding displays an increase at 2 hours after treatment with estradiol.

@@

jg.plotScatter<-function(peaks,samples,yaxis,samplesCombinations,noYLabel=FALSE)
{
    peaks$count <- 1
    peaks_aggregate <- aggregate(count ~ ., peaks, FUN = sum)
    colormap<-rainbow(255,start=0,end=4/6)
    colormap<-rev(colormap)
    peaks_aggregate$Col <- colormap[as.numeric(cut(log(peaks_aggregate$count,2),breaks=255))]
    peaks_aggregate<-peaks_aggregate[order(peaks_aggregate$count),]
    plot(log(peaks_aggregate[,c(1,2)]), col=peaks_aggregate$Col,pch=20, cex=0.3, xlim=c(0,7),ylim=c(0,7),axes=FALSE, xlab="",ylab="")
    if (samples > 1|| noYLabel==TRUE) {Axis(side=2, labels=FALSE)} else {
        Axis(side=2, labels=TRUE)
        mtext("log(Counts)", side=2, line=3)
    }
    if (yaxis !=TRUE ) {Axis(side=1, labels=FALSE)} else {
        Axis(side=1, labels=TRUE,ylab="Log(Counts)")
        mtext("log(Counts)", side=1, line=3)
    }
    text(1.5,6.5,paste0(samplesCombinations[,samples][1],"-",samplesCombinations[,samples][2]),cex=1.5)
    sampleCor<-cor(log(peaks[1]),log(peaks[2]))
    text(2,6.0,paste0("Correlation = ",signif(sampleCor,3)),cex=1.0)
    abline(a=0,b=1,col="grey")
    return(cor(log(peaks_aggregate[,c(1,2)])))
}

@@

Comparison of log(Counts) for binding sites was under taken to confirm reproducibility. The data with the lowest correlation is shown and was seen between Replicate 2 and Repelicate 3 in the control condition.

@@

H4k12ac occupancy profile before and after treatment with E2 shows a general increase around transcription start sites (TSS).

@@

Comparison of fold-change of ER binding before and after treatment with estradiol. MA plot of ER binding after normalisation to CTCF binding displays a significant increase in ER binding at 45 minutes after treatment with estradiol.

@@

Comparison of log(Counts) for binding sites was under taken to confirm reproducibility. The data with the lowest correlation is shown and was seen between Replicate 1 and Replicate 3 in the control condition.
